Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:07	12:26:29	(Wed 7.Mar)

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA
\end{itemize}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to {\LaTeX}}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\bibliography{../../Library/library}

@@

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

@@

% that's all folks
\end{document}

>>>>

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar 
\end{itemize}

@@

\bibliographystyle{IEEEtran}
\bibliography{../../Library/library}

% End up doing this:
% \begin{thebibliography}{1}
% 
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to {\LaTeX}}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
% 
% \end{thebibliography}

@@

\vfill

\begin{IEEEbiography}{Noname dude}
He doesn't exist.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Jo Inge Buskenes}
Not in at the moment.
\end{IEEEbiographynophoto}

%\newpage

% \begin{IEEEbiographynophoto}{Jo Inge Buskenes}
% Not in at the moment.
% \end{IEEEbiographynophoto}

@@

\end{document}
